A Web-Based Data Visualization Platform for MATSim

### 2020-05-15 src/paper.tex
rename figs

\begin{figure}
\centering
\includegraphics[width=3.25in]{fig-dashboard.png}
\caption{Project dashboard}\label{F1}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=3.25in]{fig-odflow.png}
\caption{Origin/Destination flows}\label{Fod}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3.25in]{fig-linkvols.png}
\caption{Link volume summary}\label{Flinkvols}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3.25in]{fig-transit.png}
\caption{Transit depiction}\label{Ftransit}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3.25in]{fig-sankey.png}
\caption{Mode shift diagram}\label{Fsankey}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3.25in]{fig-emissions.png}
\caption{Mode shift diagram}\label{Femissions}
\end{figure}

@@

\begin{enumerate}
\item[(i)] A vehicle flow simulation, showing individual vehicle agents in real-time on the network. (Figure~\ref{Fanim})
\end{enumerate}

\begin{figure}
\centering
\includegraphics[width=3.25in]{fig-animation.png}
\caption{Vehicle animation}\label{Fanim}
\end{figure}

@@

>>>>

\begin{figure}
\centering
\includegraphics[width=3.25in]{fig-1.png}
\caption{Project dashboard}\label{F1}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=3.25in]{fig-2.png}
\caption{Origin/Destination flows}\label{Fod}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3.25in]{fig-3.png}
\caption{Link volume summary}\label{Flinkvols}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3.25in]{fig-4.png}
\caption{Transit depiction}\label{Ftransit}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3.25in]{fig-5.png}
\caption{Mode shift diagram}\label{Fsankey}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3.25in]{fig-6.png}
\caption{Emissions plot}\label{Femissions}
\end{figure}

@@

\item[(i)] A vehicle flow simulation, showing individual vehicle agents in real-time on the network. (Figure~\ref{Fanim})

\begin{figure}
\centering
\includegraphics[width=3.25in]{fig-7.png}
\caption{Vehicle animation}\label{Fanim}
\end{figure}

@@

\subsection{Author Contribution Statement}

The authors confirm contribution to the paper as follows: study conception and
design: Billy Charlton, Janek Laudan; data collection: Billy Charlton; analysis and
interpretation of results: Billy Charlton, Janek Laudan; draft manuscript
preparation: Billy Charlton. All authors reviewed the results and approved
the final version of the manuscript.
